Applied Measure Theory for Probabilistic Modeling

### 2022-05-23 paper/paper.tex
edits
update Sticky PDMP reference

A very common special case of superposition is a \href{https://en.wikipedia.org/wiki/Spike-and-slab_regression}{\emph{spike and slab prior}}, a mixture of a \href{https://en.wikipedia.org/wiki/Dirac_measure}{\emph{Dirac measure}} (a point mass) with a continuous measure. 
This is useful for sparse Bayesian modeling, as implemented in the \emph{sparse ZigZag sampler}, described in \cite{arxiv2103.08478} and implemented in \cite{https://doi.org/10.5281/zenodo.3931118} using \verb|MeasureTheory|.

@@

An alternative parameterization of a multivariate Gaussian is in terms of its \href{https://en.wikipedia.org/wiki/Precision_(statistics)}{\emph{precision matrix}}, $\Lambda = \VV[\bX]^{-1}$. Similarly to above, we'll write $\lambda$ for the lower Cholesky factor of $\Lambda$, so $\lambda \lambda^t = \Lambda$. The parameterization is then specified by
\[
\bZ = \lambda(\bX - \mu)\ .
\]

>>>>

A very common special case of superposition is a \href{https://en.wikipedia.org/wiki/Spike-and-slab_regression}{\emph{spike and slab prior}}, a mixture of a \href{https://en.wikipedia.org/wiki/Dirac_measure}{\emph{Dirac measure}} (a point mass) with a continuous measure. 
This is useful for sparse Bayesian modeling, as implemented in the \emph{sparse ZigZag sampler}, described in \cite{bierkens2021sticky} and implemented in \cite{https://doi.org/10.5281/zenodo.3931118} using \verb|MeasureTheory|.

@@

An alternative parameterization of a multivariate Gaussian is in terms of its \href{https://en.wikipedia.org/wiki/Precision_(statistics)}{\emph{precision matrix}}, $\Lambda = \VV[\bX]^{-1}$. Similarly to above, we'll write $\lambda$ for the lower Cholesky factor of $\Lambda$, so $\lambda \lambda^t = \Lambda$. The parameterization is then specified by
\[
\bZ = \lambda\,(\bX - \mu)\ .
\]
